sampbias, a method for quantifying geographic sampling biases in species distribution data

### 2020-07-31 appendix_S1.Rmd
notes appendix S1

@@

@@

```{r, echo = FALSE, fig.cap="The bias weights ($w$) defining the effects of each bias factor estimated from data sets with differing density of occurrence records across the study area. Datasets generated by random simulation of records across Borneo (no bias)."}
plo <- dat %>%  filter(type == "simulated") %>%
    mutate(bias = fct_reorder(.data$bias, .data$posterior_estimate, .fun = median, .desc = FALSE))

@@

@@

```{r, out.width = "6in", fig.cap = "Projected bias surface for randomly sampled points across Borneo, from a random replicate."}

knitr::include_graphics(path = "ms_figures/figure_projection_empirical_simulation.jpg")

>>>>

REWRITE THIS PART TO DEAL WITH THE NEW TYPE OF OUTPUT FILES

@@

REDO WITH THE NEW RESULTS

@@

```{r, echo = FALSE, fig.cap="The bias weights ($w$) defining the effects of each bias factor estimated from data sets with differing density of occurrence records across the study area. Datasets generated by random simulation of records across Borneo (no bias)."}

Here a boxplot comparing the results form the empirical analyses with the ones fromt he randomly simulated analyses

plo <- dat %>%  filter(type == "simulated") %>%
    mutate(bias = fct_reorder(.data$bias, .data$posterior_estimate, .fun = median, .desc = FALSE))

@@

Here a histogram of the weight estimates

@@
